---
title: "Association"
author: "Raphael"
date: "7/21/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Importing the libraries and previewing the data 

```{r}
#install.packages('arules')
library(arules)
```


## READING DATA
```{r}
df =read.transactions("http://bit.ly/SupermarketDatasetII", sep = ",")
```

### Checking the data
```{r}
head(df)
```

```{r}
tail(df)
```


```{r}
summary(df)
```


### Cleaning the data
```{r}
# Previewing our first 5 rows
#
inspect(df[1:5])
```


## Association Rules
```{r}
items = as.data.frame(itemLabels(df))
colnames(items) <- "Item"
head(items, 5)  
```


```{r}
# Exploring the frequency of some articles 
itemFrequency(df[, 8:10],type = "absolute")
round(itemFrequency(df[, 8:10],type = "relative")*100,2)
```

```{r}
# Displaying top 5 most common items in the dataset 
# 
par(mfrow = c(1, 2))
# plot the frequency of items
itemFrequencyPlot(df, topN = 5,col="darkgreen")
itemFrequencyPlot(df, support = 0.1,col="darkred")
```

```{r}
# Building a model based on association  
ass = apriori (df, parameter = list(supp = 0.001, conf = 0.8))
ass
```


```{r}
# Ordering the rules by level of confidence
ass = sort(ass, by="lift", decreasing=TRUE)
inspect(ass[1:10])
```

```{r}
# Ordering these rules by level of confidence
ass = sort(ass, by="confidence", decreasing=TRUE)
inspect(ass[1:10])
```

## RECOMMENDATIONS

1. The top 3 purchased items were: mineral water, eggs, pasta,

2. Judging by the confidence interval, cake, eggs, pasta, meatballs and mineral water should be placed in aisles that are closer to each other since there 

3. Foods high in protein should also be placed  together since customers tend to purchase them together
